### 2018-09-13 Paper/Paper.tex
Added references to derivation of model

\section{Model}
The laser cavity is treated as the composition of five independent process---gain, nonlinearity, loss, dispersion, and modulation. Expressions for each component will be derived from the  generalized nonlinear Schr\"{o}dinger equation \cite{agrawal, ferreira, shtyrina, yarutkina},
\begin{align}
\label{eq:nlse}
\pdiff{A}{z} = - i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
\end{align}
where $A$ is the complex amplitude of the pulse, $\beta_2$ and $\beta_3$ are the second and third order dispersion coefficients respectively, $\gamma$ is the coefficient of nonlinearity, $g(A)$ is the gain, and $\alpha$ is the loss of the fiber.

\subsection{Gain}
Within the Er-doped gain fiber the other four processes are assumed to be negligible, and so \eqref{eq:nlse} reduces to
\begin{align}
\label{eq:gainde}
\pdiff{A}{z} = \frac{1}{2} g(A) A
\end{align}
with
\begin{align*}
g(A) &= \frac{g_0}{1 + E / \Es},
\end{align*}
where $g_0$ is a small signal gain, $\Es$ is the energy at which the gain begins to saturate, and \begin{align*}
E = \int_{-\infty}^\infty |A|^2 \, dT,
\end{align*}
is the energy of the pulse \cite{bohun, yarutkina}. We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. Taking
\begin{align*}
\pdiff{A}{z} = \frac{1}{2} \cdot \frac{g_0 A}{1 + E / \Es},
\end{align*}
multiplying by $\bar{A}$, the complex conjugate of $A$, and then adding the complex conjugate gives
\begin{align*}
\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es},
\end{align*}
which after integrating becomes
\begin{align*}
\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
\end{align*}
For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly. A closed form of the energy can be found by separating and integrating yielding
\begin{align}
\label{eq:energy}
E(z) = \Es W_0 \left( \frac{E_0}{\Es} e^{E_0 / \Es} e^{g_0 z} \right),
\end{align}
where $W_0$ is the Lambert $W$ function. However, only the exiting energy is of interest, thus \eqref{eq:energy} can be written as
\begin{align*}
E' = \Es W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right),
\end{align*}
where $E$ is the energy of the incoming pulse, and $E'$ is the energy after traveling through the length of the gain fiber. Since $E \sim |A|^2$ the gain in terms of the amplitude is given by
\begin{align}
\label{eq:gain}
G(A) &= \left[ \frac{\Es}{E} W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right) \right]^{1/2} A.
\end{align}

@@

\subsection{Loss}
Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to the circuit. It will be assumed all loss occurs at a particular point in the circuit because of the extremely high reflectivity of the fiber the optical loss is negligible compared to the output coupler loss ***cite. The loss is then given as
\begin{align*}
L(A) &= C e^{- \alpha L}A,
\end{align*}
where $C$ is the loss due to the output coupler.

\subsection{Dispersion}
The dominant dispersion is due to the chirped fiber Bragg grating (CFBG)---the dispersion due to the fiber is negligible in comparison \cite{agrawalother}. The dispersive pieces of \eqref{eq:nlse} give
\begin{align}
\label{eq:disp}
\pdiff{A}{z} = -i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T},
\end{align}
but, the third order effects of dispersion will be neglected ***cite. Although, under some circumstances they may need to be considered since the CFBG is highly dispersive \cite{litchinitser}. Taking the Fourier transform of \eqref{eq:disp} gives
\begin{align*}
\pdiff{\FT{A}}{z} &= \frac{1}{2} i \beta_2 \omega^2 \FT{A}.
\end{align*}
The Fourier transform of $A$ can be found by integrating and
\begin{align*}
D(A) &= \FTi{e^{i \frac{1}{2} \beta_2 \omega^2 L_D} \FT{A}}
\end{align*}
is the effect of the CFBG on the pulse.

>>>>

\section{Model}
The laser cavity is treated as the composition of five independent process---gain, nonlinearity, loss, dispersion, and modulation. Expressions for each component will be derived from the  generalized nonlinear Schr\"{o}dinger equation \cite{agrawal2013, ferreira, shtyrina, yarutkina},
\begin{align}
\label{eq:nlse}
\pdiff{A}{z} = - i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
\end{align}
where $A$ is the complex amplitude of the pulse, $\beta_2$ and $\beta_3$ are the second and third order dispersion coefficients respectively, $\gamma$ is the coefficient of nonlinearity, $g(A)$ is the gain, and $\alpha$ is the loss of the fiber.

\subsection{Gain}
Within the Er-doped gain fiber the other four processes are assumed to be negligible, and so \eqref{eq:nlse} reduces to
\begin{align}
\label{eq:gainde}
\pdiff{A}{z} = \frac{1}{2} g(A) A
\end{align}
with
\begin{align*}
g(A) &= \frac{g_0}{1 + E / \Es},
\end{align*}
where $g_0$ is a small signal gain, $\Es$ is the energy at which the gain begins to saturate, and \begin{align*}
E = \int_{-\infty}^\infty |A|^2 \, dT,
\end{align*}
is the energy of the pulse \cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina}. We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. Taking
\begin{align*}
\pdiff{A}{z} = \frac{1}{2} \cdot \frac{g_0 A}{1 + E / \Es},
\end{align*}
multiplying by $\bar{A}$, the complex conjugate of $A$, and then adding the complex conjugate gives
\begin{align*}
\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es},
\end{align*}
which after integrating becomes
\begin{align*}
\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
\end{align*}
For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly. A closed form of the energy can be found by separating and integrating yielding
\begin{align}
\label{eq:energy}
E(z) = \Es W_0 \left( \frac{E_0}{\Es} e^{E_0 / \Es} e^{g_0 z} \right),
\end{align}
where $W_0$ is the Lambert $W$ function. However, only the exiting energy is of interest, thus \eqref{eq:energy} can be written as
\begin{align*}
E' = \Es W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right),
\end{align*}
where $E$ is the energy of the incoming pulse, and $E'$ is the energy after traveling through the length of the gain fiber. Since $E \sim |A|^2$ the gain in terms of the amplitude is given by
\begin{align}
\label{eq:gain}
G(A) &= \left[ \frac{\Es}{E} W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right) \right]^{1/2} A.
\end{align}

@@

\subsection{Loss}
Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to the circuit. The loss is then given as
\begin{align*}
L(A) &= C e^{- \alpha L}A,
\end{align*}
where $C$ is the loss due to the output coupler.

\subsection{Dispersion}
The dominant dispersion is due to the chirped fiber Bragg grating (CFBG). The dispersion due to the fiber is negligible in comparison---a $10$cm chirped grating can provide as much dispersion as $300$km of fiber \cite{agrawal2002}. The dispersive terms of \eqref{eq:nlse} give
\begin{align}
\label{eq:disp}
\pdiff{A}{z} = -i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T},
\end{align}
however, the third order effects of dispersion will be neglected \cite{agrawal2013, ferreira}. Although, under some circumstances they may need to be considered since the grating is highly dispersive \cite{agrawal2013, litchinitser}. Taking the Fourier transform of \eqref{eq:disp} gives
\begin{align*}
\pdiff{\FT{A}}{z} &= \frac{1}{2} i \beta_2 \omega^2 \FT{A}.
\end{align*}
The Fourier transform of $A$ can be found by integrating and thus,
\begin{align*}
D(A) &= \FTi{e^{i \frac{1}{2} \beta_2 \omega^2 L_D} \FT{A}}
\end{align*}
is the effect of the grating on the pulse.
